Fluid structure interaction with ETVF

### 2021-04-11 manuscript/paper.tex
Manuscript: Add a bit introduction and write one result

@@

The force acting on the fluid particles is now computed from the pressure set
using the adami boundary conditions and density set consequently. We mark
particles comprising the solid as `a` and fluid as `i`, and the force acting
on the fluid particle `i` is given as

\begin{equation}
  f_i^s = -m_i \Sum_{a} m_a \bigg(\frac{p_i}{\rho_{i}^2} +
  \frac{p_a}{\rho_{a}^2} + \Pi_{ia} \bigg) \nabla_{i} W(x_{ia})
\end{equation}

@@

\begin{equation}
  f_a^F = -m_i \Sum_{a} m_a \bigg(\frac{p_a}{\rho_{a}^2} +
  \frac{p_i}{\rho_{i}^2} + \Pi_{ai} \bigg) \nabla_{a} W(x_{ai})
\end{equation}

@@

@@

We can see the problem description in figure XXX. The water column height is
2m and has a width of 0.5m. An aluminum plate of thickness 0.05m is placed at
the bottom of the tank.The material properties of the aluminum are as follows,
a density of 2700 kg/m^3, an Young’s modulus of $E = 6.75 \times 10^{10} Pa$,
and the Poisson’s ratio $\nu = 0.34$. The plate is clamped on both the
sides. Once the simulation begins, a sudden hydrostatic pressure force is
applied on the aluminum plate. With time the plate oscillates and comes to
rest. We compare the static displacement of the plate with the analytical
solution.

@@

>>>>

Some FSI introduction. Its importance in different fields. Its applications so
far.

In modelling FSI problems, there are mainly two ways to handle the fluid and
structures modelling. One way is to model the fluid part with mesh based
scheme and solids part also with mesh based scheme. Like how (cite many papers
which have done this). Or fluid part is modelled with a particle based scheme
and the structures part with a mesh based scheme (Cite articles which have
done this). One more way is to model both the phases using particle based
schemes. In this paper we use particle based method to model both the phases.

Recently there has been very good work on modelling fsi with particle based
methods. Specific to particle based modelling, the fluid is modelled with SPH,
and structure is modelled with different numerical method. Few articles which
have done in this regard are as follows, citet{hosseini2009particle} has
modelled the structure part using EBG method, then \citet{wu2016coupled}
modelled it with DEM, \citet{ng2020coupled} modeled it using volume
compensated particle method (VCPM), \citet{peng2021coupling} modeled it with
RKPM, citet{zhang2021deltasph} modeled it with Smoothed Point Interpolation
Method (SPIM).

Recently there have been heavy improvements to basic SPH methodology in
modelling fluid problems. Schemes such as $\delta$ SPH, $\delta +$ SPH, TVF
for internal flows and GTVF for external flows is been proposed. Also, many
new strategies were proposed to in overcoming the particle homogeneity
problem, such as IPST, which is applied in \cite{IPST paper}. Also these
improvements take care of tensile instability problem too. Another variant of
SPH is ISPH, todoin{please cite some ISPH papers here}.

Using only SPH, articles have been proposed where we model both the phases
only using SPH. To note some, \citet{He2017coupled} has modelled the fluid
part with WCSPH, \citet{Sun2019study} with delta sph,
\citet{zhan2019stabilized} with WCSPH but applied to 3d problems with GPU. All
these schemes use TLSPH as to model the structure part. And papers by Abbas use
usual Gray equations to model the structures part.

Recently {cite our paper ETVF} has been proposed as an another extension to
TVF to model both fluid and structures part. In the current work we couple
purely Eulerian SPH based schemes to model the FSI problems. We take advantage
of the accuracy of the ETVF scheme proposed in modelling the fluids. ETVF
scheme deals with tensile instability in both fluid and solid inherently.

@@

The force acting on the fluid particles is now computed from the pressure set
using the adami boundary conditions and density set consequently. We mark
particles comprising the solid as $a$ and fluid as $i$, and the force acting
on the fluid particle $i$ is given as

\begin{equation}
  f_i^s = -m_i \sum_{a} m_a \bigg(\frac{p_i}{\rho_{i}^2} +
  \frac{p_a}{\rho_{a}^2} + \Pi_{ia} \bigg) \nabla_{i} W(x_{ia})
\end{equation}

@@

\begin{equation}
  f_a^F = -m_i \sum_{a} m_a \bigg(\frac{p_a}{\rho_{a}^2} +
  \frac{p_i}{\rho_{i}^2} + \Pi_{ai} \bigg) \nabla_{a} W(x_{ai})
\end{equation}

@@

The papers we have followed for the benchmarks are
\citet{sun2021accurate}, \citet{yang2016numerical}, \citet{Sun2019study},
\citet{He2017coupled}, \citet{khayyer2018enhanced}, \citet{sun2015numerical},
\citet{wang2020scale}, \citet{peng2021coupling}, \citet{zhang2021deltasph},
\citet{zhan2019stabilized}, \citet{khayyer2021multi},
\citet{long2021coupling}, \citet{ng2020coupled},

@@

We can see the problem description in figure XXX. The water column height is
2m and has a width of 0.5m. An aluminum plate of thickness 0.05m is placed at
the bottom of the tank.The material properties of the aluminum are as follows,
a density of 2700 $kg/m^3$, an Young’s modulus of $E = 6.75 \times 10^{10} Pa$,
and the Poisson’s ratio $\nu = 0.34$. The plate is clamped on both the
sides. Once the simulation begins, a sudden hydrostatic pressure force is
applied on the aluminum plate. With time the plate oscillates and comes to
rest. We compare the static displacement of the plate with the analytical
solution.

@@

\subsection{High speed impact of an elastic aluminum wedge on undisturbed
  water surface}
\label{sec:wedge-impact-on-water}

Here we simulate a high speed elastic aluminum wedge impacting on undisturbed
water surface. This benchmark was dealt in
{A $\delta$ SPH-SPIM coupled method for fluid-structure interaction problems} and
{abbas khayyer} papers.
This is an attractive benchmark as it has an semi-analytical solution.

A fluid of length 6 m and a height of 2.2 m is settled inside a tank of length
6m and height 4m which gives rise to a pressure distribution of a hydrostatic
tank. Into this hydrostatic tank a wedge of length 0.6m and a thickness of
0.04m is been dropped with a velocity of 30 m/s. The wedge angle is 10
degrees. Please see figure \ref{fig:half-wedge-deformable} for visual clarity.

The initial particle spacing is set as 0.005m and the total number of
particles combining the wedge, tank and fluid is TOBEDONE. The density of the
fluid is taken as 1000 $kg/m^3$. The material properties of the wedge are as
follows: density of 2700 $Kg/m^3$, Young's modulus of 6.75 1e10 $N/m^2$ and a
Poisson ratio of 0.34. An artificial viscosity $alpha$ of 0.1 is used for
fluids and 1 for solid phase.

In figure \ref{wedge-entering-the-tank}, at different time stamps, we plot the
pressure fields of water and sigma 00 if the flexible wedge. (We need to give
some physical insight of what is expected and what is been observed, provided
our simulations are correct)

A total of three points are marked on the wedge for a qualitative validation.
In figure \ref{point-A-wedge-displacement}, we plot the displacement of point
A with time, and compared with Abbhas and and the semi analytical solution of
scolon 2004. Similarly at point B and point C we compare the pressure of the
current scheme with the one provided with Abbas and the semi analytical
solution. It can be seen that the current scheme is able to produce the
results with a reasonable accuracy.
